Eagle: multi-locus association mapping on a genome-wide scale made routine

### 2019-08-12 BioinformaticsRevison/bioinformaticspaper.tex
STill making changes

\section{Discussion/Conclusion}
Eagle is a new linear mixed model based method (and R package) for multi-locus association mapping. It advances the state of association mapping in several ways. 
First, its computational footprint is much smaller than other multi-locus implementations. Eagle makes multi-locus analysis 
practical, even when the datasets are large. Second, the results from
 Eagle are immediately interpretable. They are the set of SNPs in strongest association with the trait where 
each SNP identifies a separate genomic region of interest. Third, it treats association mapping as a model selection problem, avoiding 
 multiple testing issues. 
 As we saw in the simulation study, Eagle has considerably higher power than single-locus methods but is comparable in run time.
Also, when analysing the mouse data, Eagle found more than double the SNP-trait associations than 
with single-locus association mapping, the method of choice. \textcolor{red}{Furthermore, because we converted the SNP dosages of the 
original study into genotypes and focusing our analyses on these data, the validity of the extra findings can be confirmed 
against the original findings}. These extra findings were all true.

@@

>>>>

\section{Discussion/Conclusion}
Eagle is a new linear mixed model based method (and R package) for multi-locus association mapping. It advances the state of association mapping in several ways. 
First, its computational footprint is much smaller than other multi-locus implementations. Eagle makes multi-locus analysis 
practical, even when the datasets are large. Second, the results from
 Eagle are immediately interpretable. They are the set of SNPs in strongest association with the trait where 
each SNP identifies a separate genomic region of interest. Third, it treats association mapping as a model selection problem, avoiding 
 multiple testing issues. 
 As we saw in the simulation study, Eagle has considerably higher power than single-locus methods but is comparable in run time.
Also, when analysing the mouse data, Eagle found more than double the SNP-trait associations than 
with single-locus association mapping, the method of choice. \textcolor{red}{Furthermore, because we converted the SNP dosages of the 
original study into genotypes and focused our analyses on these data, the validity of the extra findings were able to  be confirmed 
against the original findings}. These extra findings were all found to be true.

@@

\textcolor{red}{
Upon submitting our paper for review, a more recent multi-locus association mapping method, FarmCPU(), was brought to our attention. 
It is an unorthodox approach. Instead of working with a single model, results are passed back and forth between two models, 
a fixed effects model and a random effects model. Measures of association are obtained from the fixed effect model, which in turn 
help define pseudo-QTN from the random effects model. Conversely, pseudo-QTN found from the random effects model are passed 
back to the fixed effect model to better refine the measures of association.  The method involves multiple rounds of genome-wide 
testing. Out of interest, we reanalysed the mouse data with FarmCPU.  Runtimes were around five times longer for FarmCPU than 
Eagle.  Interestingly, FarmCPU found the same number of associations, 106,  as Eagle$^{optimal}$, but the findings were only the 
same for 11 of the traits.  For 14 (14) traits, Eagle (FarmCPU) found more associations.  Where the new findings from Eagle could 
be confirmed, of the 18 new associations found by FarmCPU, we were unable to confirm 10 using the results from the original study. 
The two methods differ significantly in their implementation. FarmCPU is not an R package but a set of R scripts. We had 
no problem in using the scripts but this may not be true for non-R users. In contrast, Eagle has been developed for ease-of-use.
Eagle is an R package but its browser-based GUI makes it accessible to all.
}

### 2019-08-12 BioinformaticsRevison/supmaterials.tex
STill making changes

\hspace{1mm} SNPs fitted $^e$      &    All/multiple      &    All       &   All        &      All          &  Multiple          &  Multiple              &   Single   &  Single   \\  [0.15cm]

\hspace{1mm}  Selection type             & Model   & Variable  &  Variable &  Variable  &  Model  &  Variable & Variable  & Variable \\  [0.15cm]

\hspace{1mm} Threshold free      &    Yes     &  No    &  No         &    No               &     Yes       &  No              &  No   & No      \\  [0.15cm]  \hline

>>>>

\hspace{1mm} SNPs fitted $^e$      &    All/multiple      &    All       &   All        &      All          &  Multiple          &  Multiple              &   Single   &  Single   \\  [0.15cm]  \hline
